---
title: "Hello R"
author: "Misgana  Bekele"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 8
    fig_height: 6
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen dataset has 1846 rows and 3 columns. It included three variable: dataset, x, and y.

### Exercise 2



# First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

# next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3



# Plot x vs. y for star dataset 

```{r plot-star}
star_data <- datasaurus_dozen %>% filter(dataset == "star") 
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()

```

# correlation coefficent 
 
```{r cor-star}
star_data %>% summarize(r = cor(x, y))

```

### Exercise 4

# Plot x vs. y for circle dataset

```{r}
circle_data <- datasaurus_dozen %>% filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + geom_point()


```



# correlation coefficient
```{r}
circle_data %>% summarize(r = cor(x, y))

```

### Exercise 5

# Plot all datasets at once

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

# correlation coefficients for all datasets
```{r}
datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarize(r = cor(x, y))
```

